\documentclass[a4paper, 12pt]{book}

\usepackage{hyperref}

\begin{document}

\pagenumbering{roman}
\title{The Malevolent Ingenuity of Preprocessor Metaprogramming in C}
\author{Temirkhan Myrzamadi}
\date{\today}
\maketitle

\tableofcontents

\newpage

\section{Foreword}

The macro system is probably the most contradictory feature of C: it provides a way to
\href{https://en.wikipedia.org/wiki/Extensible_programming}{extend} the host programming
language with new syntactical constructs, thus forcing some ill-formed programs fail
to compile, but nevertheless is an increasingly treacherous technology, being able to
potentially cause a numerous amount of bugs out of nothing.

This book was derived by my continuous experiments with the preprocessor: I have implemented
some of the concepts of functional programming, including
\href{https://en.wikipedia.org/wiki/Algebraic_data_type}{algebraic data types (ADTs)} with
\href{https://en.wikipedia.org/wiki/Proof_by_exhaustion}{exhaustive}
\href{https://en.wikipedia.org/wiki/Pattern_matching}{pattern matching},
\href{https://en.wikipedia.org/wiki/Parametric_polymorphism}{parametric polymorphism},
\href{https://en.wikipedia.org/wiki/Kind_(type_theory)}{higher-kinded types}, and
\href{https://en.wikipedia.org/wiki/Generalized_algebraic_data_type}{generalised ADTs}, as
well as from the world of object orientation: classes,
\href{https://en.wikipedia.org/wiki/Dynamic_dispatch}{dynamic dispatch}, and all the coherent
stuff: \href{https://en.wikipedia.org/wiki/Type_introspection}{type introspection}, type-safe
error handling facilities and more.

So what I want to say: writing macros is an art. Macros, overall, can even be considered as
computer languages on their own, with custom syntax, given by their signatures, and
semantics, defined by their bodies. In this book, I have accomplished my best concerning
the development of macros, and I do believe that it will advance a reader to a completely
new dimension of metaprogramming, show how much more beautiful macro interfaces can be, and
develop the intuition in such a tricky topic.

\newpage

\section{Audience}

This book is targeted mostly at programmers who feel comfortable with the C programming
language. No additional prerequsites are required, though, some experience with macros might
be helpful.

\newpage

\section{Outline}

So to sum up everything discussed above, the aim of this book is to show how to achieve all
the benefits of the macro system of C and to overcome its drawbacks as much as possible. It
comprises of lots of examples, case studies, various techniques and tricks. All the
explanations and code blocks are C11-compliant, unless otherwise stated.

Now let's give a short outline of all the chapters:

\newpage

\chapter{Introduction}
\chapter{Writing the Preprocessor from Scratch}
\chapter{Case Study: Parsing Command-Line Arguments}

\end{document}
